Gravity model and word2vec

### 2021-01-07 paper/current/notes/2021-0105-word2vec-vs-gravity-model/main.tex
edit the terms that we have been used in the main paper

Let us approach the connection by initially focusing on the gravity model.
Suppose that flow of people between $N$ locations. The gravity model models the flow by
\begin{align}
    T_{ij} = G M_i M_j f(d_{ij}), \label{eq:gravity_model}
\end{align}
where $T_{ij}$ is the flow from location $i$ to $j$, $M_i$ is a mass term corresponding to population of $i$, $d_{ij}$ is a distance between locations $i$ and $j$,
$f$ is a decreasing function with respect to $d_{ij}$, and $G$ is a constant.
That the gravity model implicitly assumes that the flow is symmetric, \ie $T_{ij}=T_{ji}$, which ensures the stationarity in population $M_{i}$.
The choice of distance measure $d_{ij}$ is entirely unconstrained; it can be the euclidean distance, or even pseudo distance measure that does not satisfy the axioms for metric space.
In the following, we refer to a measure of dissimilarity as distance.

>>>>

Let us approach the connection by initially focusing on the gravity model.
Suppose that flow of people between $N$ locations. The gravity model models the flow by
\begin{align}
    \hat{T_{ij}} = C m_i m_j f(r_{ij}), \label{eq:gravity_model}
\end{align}
where $\hat{T_{ij}}$ is the expected flow from location $i$ to $j$, $m_i$ is the population of locations of $i$, $r_{ij}$ is a distance between locations $i$ and $j$, $f$ is a decreasing function with respect to $r_{ij}$, and $C$ is a constant.
That the gravity model implicitly assumes that the flow is symmetric, \ie $T_{ij}=T_{ji}$, which ensures the stationarity in population $M_{i}$.
The choice of distance measure $d_{ij}$ is entirely unconstrained; it can be the euclidean distance, or any kind of general distance measure.
In the following, we refer to a measure of dissimilarity as distance.
